% ---- Professional Experience ----
\section{Professional Experience}

\cvitem
{Chief Technology Officer}
{2023 -- Present}
{rangoondiscount.com}
{
    \item Designed, implemented, and managed the rangoondiscount.com website, supporting the technical foundation of the business.
    \item Managed website operations, technical planning, and business-related technology decisions.
    \item Oversaw system availability, website functionality, and ongoing improvements for business operations.
    \item Coordinated technical requirements between business needs, website implementation, and operational support.
}

\cvitem
{Freelance Researcher \& Infrastructure Engineer}
{2022 -- Present}
{Remote / Self-directed Technical Work}
{
    \item Designed and tested Linux-based infrastructure environments involving containers, networking, VPNs, routing, and service deployment workflows.
    \item Built Go-based container deployment tools using CLI and REST API patterns, focusing on Docker-based service execution and infrastructure automation.
    \item Investigated Docker networking, container lifecycle behavior, service exposure, logs, runtime status, and container removal workflows.
    \item Performed system-level troubleshooting across host networking, container networking, NAT, firewalling, and VPN configurations.
    \item Developed technical documentation and project READMEs explaining architecture, usage, API endpoints, and manual test plans.
}

\cvitem
{Part-time Lecturer}
{2021 -- 2022}
{Auston University}
{
    \item Taught Network Forensics, covering network evidence interpretation, traffic investigation, and the impact of modern network technologies on forensic analysis.
    \item Taught Network Defense, covering intrusion detection, firewall techniques, security countermeasures, and defensive network design.
    \item Guided students in evaluating network security techniques and applying defensive strategies to secure information systems.
    \item Connected theoretical networking concepts with practical security, investigation, and defense scenarios.
}

\cvitem
{Ph.D. Researcher}
{2017 -- 2019}
{Kanazawa University, Japan}
{
    \item Conducted research on next-generation networking, name-based communication, network privacy, and security in distributed systems.
    \item Designed and evaluated privacy-preserving Named Data Networking strategies using Public Key Encryption with Keyword Search.
    \item Analyzed protocol-level behavior, forwarding strategies, and performance trade-offs in content-centric network architectures.
}

\cvitem
{Lecturer}
{2012 -- 2017}
{Yangon Technological University, Myanmar}
{
    \item Taught Data Communication and Networking, including network models, TCP/IP protocol suite layers, and services provided by each network layer.
    \item Taught Introduction to Computer Systems, covering fundamentals of computer processing, hardware, and software.
    \item Supervised Master’s degree students in academic and technical project work.
    \item Supported students in understanding networking, systems, and computing fundamentals.
}

\cvitem
{Network Infrastructure \& Virtualization Experience}
{}
{Academic / Professional Infrastructure Work}
{
    \item Designed, installed, configured, monitored, logged, debugged, and maintained campus network infrastructure.
    \item Worked with VMware vSphere virtualization environments.
    \item Worked with Red Hat Enterprise Virtualization for infrastructure and virtualized system management.
    \item Performed network monitoring, troubleshooting, and operational support across academic infrastructure environments.
}