% ---- Projects ----
\section{Selected Projects}

\cvitem
{dockpilot}
{2026}
{Go, Docker, REST API, CLI --- \href{https://github.com/kyitharko/dockpilot}{github.com/kyitharko/dockpilot}}
{
    \item Developed a lightweight Go-based container deployment tool for managing individual services through Docker-based workflows.
    \item Implemented CLI and REST API interfaces for deploying, removing, listing, checking status, and retrieving logs from managed containers.
    \item Designed a shared engine layer so CLI commands and API handlers use consistent container management logic.
    \item Added built-in service presets for MongoDB, PostgreSQL, Redis, and Nginx to support repeatable local infrastructure deployment.
    \item Documented API endpoints, response formats, error codes, container naming conventions, and manual usage examples.
}

\cvitem
{stackpilot}
{2026}
{Go, YAML, Docker orchestration, REST API client --- \href{https://github.com/kyitharko/stackpilot}{github.com/kyitharko/stackpilot}}
{
    \item Developed a higher-level stack orchestration tool that reads YAML service definitions and delegates container execution to dockpilot.
    \item Implemented stack validation, service dependency resolution, and deployment ordering using dependency-graph concepts.
    \item Designed separation of responsibilities between stackpilot and dockpilot: stackpilot handles YAML, validation, and dependency order; dockpilot handles Docker execution.
    \item Added stack deploy, remove, status, and validate workflows for multi-service application environments.
    \item Documented manual test scenarios including successful deployment, idempotency, removal order, volume removal, cycle detection, and dockpilot-unreachable cases.
}