% ---- Education & Publications ----
\section{Education}

\cvitem
{Ph.D. in Information Science / Next Generation Networks}
{2017 -- 2019}
{Kanazawa University, Kanazawa, Japan}
{
    \item Researched distributed communication systems, name-based networking, privacy-preserving communication, and network security.
    \item Focused on next-generation Internet architectures, secure content retrieval, and privacy-preserving communication in Named Data Networking.
}

\section{Selected Publications}

\cvitem
{Trapdoor Assignment of PEKS-based NDN Strategy in Two-Tier Networks}
{2021}
{IEEE Xplore. Document ID: 9394212}
{
    \item Extended PEKS-based Named Data Networking research by investigating trapdoor assignment in two-tier NDN architectures.
    \item Demonstrates research depth in privacy-preserving content retrieval, searchable encryption, and secure distributed networking.
    \item Relevant to infrastructure, security, and distributed systems roles requiring protocol-level analysis and system design.
}

\cvitem
{A PEKS-Based NDN Strategy for Name Privacy}
{2020}
{Future Internet, 12(8), 130. DOI: 10.3390/fi12080130}
{
    \item Proposed a privacy-preserving Named Data Networking strategy using Public Key Encryption with Keyword Search.
    \item Implemented and evaluated PEKS-based forwarding strategies based on NDN best-route and multicast strategies.
    \item Demonstrates research depth in network security, privacy-preserving communication, protocol-level analysis, and distributed systems.
}